%!TEX root = labo.tex

\subsubsection*{Bridges and the Spanning Tree Protocol}
Use the following resources to prepare yourself for this lab session:
\begin{enumerate}
	\item Bridging: Read about LAN switching and bridging at \url{http://docwiki.cisco.com/wiki/Internetworking_Technology_Handbook#Bridging_and_Switching}.
	\item Transparent Bridges and Spanning Tree Protocol: Read about transparent bridges and the spanning tree protocol at \url{http://docwiki.cisco.com/wiki/Transparent_Bridging}.
	\item Bridge Protocol Data Unit (BPDU): Familiarize yourself with the format of bridge protocol data units (BPDUs) by reading the information at \url{http://ericleahy.com/index.php/implementing-spanning-tree-protocol-stp/}.
	\item Configuring a PC as a Bridge: Explore the website \url{http://www.linuxfoundation.org/collaborate/workgroups/networking/bridge}, which describes the bridge-utils software package for configuring a Linux PC as a bridge.
\end{enumerate}

\newpage
\subsection*{Prelab Questions}
\begin{questions}
	\q{1}{Describe the difference between a LAN switch/bridge and a router?}
	\q{2}{What is the difference between an Ethernet switch and an Ethernet hub? Which is more suitable for a network with a high traffic load, a switch or a hub? Explain.}
	\q{3}{What motivates the use of the term “transparent” in transparent bridges?}
	\q{4}{Which role does the spanning tree protocol play when interconnecting LAN switches/bridges?}
	\q{5.a}{In the context of the IEEE 802.1d specification of the spanning tree protocol, define root bridge.}
	\q{5.b}{In the context of the IEEE 802.1d specification of the spanning tree protocol, define root port.}
	\q{5.c}{In the context of the IEEE 802.1d specification of the spanning tree protocol, define designated bridge.}
	\q{5.d}{In the context of the IEEE 802.1d specification of the spanning tree protocol, define designated port.}
	\q{5.e}{In the context of the IEEE 802.1d specification of the spanning tree protocol, define blocked port.}
	\q{6}{In the spanning tree protocol, how does a LAN switch/bridge decide which ports are in a blocking state?}
\end{questions}
